---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::knit_hooks$set(margin = function(before, options, envir) {
  if (before) par(mgp = c(1.5, .5, 0), bty = "n", plt = c(.105, .97, .13, .97))
  else NULL
})

knitr::opts_chunk$set(margin = TRUE, prompt = TRUE, comment = "#>",
                      collapse = TRUE, cache = FALSE, autodep = TRUE,
                      dev.args = list(pointsize = 11), fig.height = 3.5,
                      fig.width = 4.24725, fig.retina = 2,
                      fig.align = "center", fig.path = "README-")
```

# gadmSEA

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/gadmSEA)](https://cran.r-project.org/package=gadmSEA)

The goal of `gadmSEA` is to ease the drawing of location maps of any set of
countries from Southeast Asia. **This package contains no function and 
basically simply provides the polygons of the following 28 countries**:
Afghanistan, Bangladesh, Bhutan, Cambodia, China, India, Japan, Indonesia,
Japan, Kazakhstan, Korea, Kyrgystan, Lao PDR, Malaysia, Mongolia, Myanmar,
Nepal, North Korea, Paskistan, Papua New Guinea, the Philippines, Russia, 
Singapore, Sri Lanka, Taiwan, Tajikistan, Thailand, Uzbekistan and Vietnam. 
These polygons come from [GADM](http://www.gadm.org).


## Installation

You can install `gadmSEA` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("choisy/gadmSEA")
```


## Usage

The list of available countries can be seen with the `mcutils::dataset`
function that returns the list of the names of the data sets available in a 
given package.

```{r}
mcutils::datasets("gadmSEA")
```

The package `mcutils` can be installed from GitHub:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("choisy/mcutils")
```

To load a specific country, we can either access directly to the data set:

```{r}
vietnam <- gadmSEA::vietnam
```

or use the `utils::data` function:

```{r}
data(vietnam, package = "gadmSEA")
```

These polygons are of class `SpatialPolygonsDataFrame`:

```{r}
class(vietnam)
```

and can be plotted with the `sp::plot` corresponding method:

```{r}
sp::plot(vietnam, col = "grey")
```

