---
title: "Introduction to gadmSEA"
author: "Marc Choisy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::knit_hooks$set(margin = function(before, options, envir) {
  if (before) par(mgp = c(1.5, .5, 0), bty = "n", plt = c(.105, .97, .13, .97))
  else NULL
})

knitr::opts_chunk$set(margin = TRUE, prompt = TRUE, comment = "#>",
                      collapse = TRUE, cache = FALSE, autodep = TRUE,
                      dev.args = list(pointsize = 11), fig.height = 3.5,
                      fig.width = 4.24725, fig.retina = 2,
                      fig.align = "center", fig.path = "README-")
```

Two examples showing how we can draw a map showing the location of a country in
southeast Asia and of a set a countries in southeast Asia.

## Map highlighting 1 country

Below is the code showing how to draw a map showing the location of Vietnam.
Let's first load the needed packages:

```{r message = FALSE}
library(gadmSEA)
library(sp)       # "plot" method
library(magrittr) # %>% and %$% pipe operators
library(dplyr)    # "mutate" function and the " %>% " pipe operator
library(purrr)    # "map2" 
```

The packages `sp`, `magrittr`, `dplyr` and `purrr` can be installed from 
[CRAN](https://cran.r-project.org). Let's start by defining some colors:

```{r}
rgb2 <- function(...) rgb(..., max = 255)
blue   <- rgb2(200, 237, 255) # for the sea
grey   <- rgb2(225, 225, 225) # for the countries other than Vietnam
yellow <- rgb2(253, 252, 235) # for Vietnam
```

The plot is in 2 steps:

```{r}
# (1) first we plot the background, in blue around the country of interest:
plot(vietnam, xlab = "longitude (decimal degree)", border = NA,
              ylab = "latitude (decimal degree)", bg = blue)

# (2) then we plot the countries with yellow for Vietnam and grey for the rest:
mcutils::datasets("gadmSEA") %>%
  as.data.frame(stringsAsFactors = FALSE) %>%
  setNames("country") %>%
  mutate(col = ifelse(country == "vietnam", yellow, grey)) %$%
  invisible(map2(country, col, ~ plot(get(.x), col = .y, add = TRUE)))

# (3) finally we optionally add the axes and a box:
axis(1); axis(2); box(bty = "o")
```

## Map highlighting 14 countries

We can use the same pipeline to highlight more than one country. For example,
these countries:

```{r}
ctr <- c("vietnam", "philippines", "cambodia", "japan", "china", "thailand",
         "singapore", "indonesia", "malaysia", "taiwan", "bangladesh", "laos",
         "india", "nepal")
```

The map can be drawn with the same 3 steps as before:

```{r}
plot(vietnam, xlab = "longitude (decimal degree)", border = NA,
              ylab = "latitude (decimal degree)", bg = blue,
              xlim = c(68, 146), ylim = c(-11, 54))

mcutils::datasets("gadmSEA") %>%
  as.data.frame(stringsAsFactors = FALSE) %>%
  setNames("country") %>%
  dplyr::mutate(col = ifelse(country %in% ctr, yellow, grey)) %$%
  invisible(purrr::map2(country, col, ~ plot(get(.x), col = .y, add = TRUE)))

axis(1); axis(2); box(bty = "o")

# adding the equator and the tropic:
abline(h = c(0, 23.43695), lty = 1:2)
```

